%!TEX TS-program = latex
\documentclass{robinthesis}

\begin{thesischapter}{Cayley}{Cayley's Theorem for Pseudomonoids}
%
In its traditional form, Cayley's theorem says that every finite group
is (isomorphic to) a subgroup of one of the symmetric groups. What the
proof actually shows is that every monoid $M$ is a submonoid of the monoid
of endofunctions $|M|\to|M|$, via the function that maps the element $x\in M$
to the function $x\o-$.

A `Cayley Theorem for monoidal categories' has been used by
\citet[Proposition~1.3]{BTC} to show that every monoidal category
is monoidally equivalent to a \emph{strict} monoidal category.
It turns out that we need the corresponding theorem for
promonoidal categories; and rather than just prove another special
case, it seems wise to generalise. So the purpose of this
chapter is to state and prove a Cayley Theorem for pseudomonoids.

As motivation, we begin by reviewing the one-dimensional case,
of monoids in a monoidal category.

\section{Cayley's theorem for monoids}

I'm not aware of any literature that specifically addresses the
question of giving an analogue of Cayley's theorem for monoids
in a monoidal category, but it is a special case of a standard
construction. A monoid in the monoidal category $\V$ can be
regarded as a one-object $\V$-enriched category.\footnote{This
operation -- reimagining a monoid as a one-object category -- is often
called \emph{suspension}.} Then we can apply the enriched Yoneda
Lemmas of \citet[sections~1.9 and~2.4]{KellyEnriched} to this
$\V$-category. Since it requires some effort to extract the
specifics of the one-object case from Kelly's constructions,
we give an overview here.

Let $\V$ be a monoidal category, and let $M$ be a monoid in $\V$,
with unit $e: I\to M$ and multiplication $m: M\tn M\to M$.
%
% In the pseudomonoid case, we shall work in a Gray-monoid and use
% coherence to transfer the result to an arbitrary monoidal bicategory.
% Since this process is not entirely trivial, we shall illustrate
% the process in the one-dimensional case, where the analogous
% strategy would be to work in a \emph{strict} monoidal category $\V$.
% Thus we shall assume, for the moment, that $\V$ is strictly
% associative. (We could also take the unit to be strict, of course,
% but we do not, since it doesn't particularly help.)

The Cayley-Yoneda theorems are best stated in terms of modules:
\begin{definition}\label{def-module}
	A \emph{right $M$-module} consists of an object $X\in\V$ and a map
	\[
		x: X\tn M\to X
	\]
	such that the diagrams
	\[
	\begin{diagram}
		X\tn M\tn M & \rTo^{x\tn M} & X\tn M \\
		\dTo<{X\tn m} && \dTo>{x} \\
		X\tn M & \rTo_{x} & X
	\end{diagram}
	\quad\mbox{and}\quad
	\begin{diagram}
		X &\rTo^{\cong} & X\tn I \\
		\dTo<1 && \dTo>{X\tn e} \\
		X & \lTo_{x} & X\tn M
	\end{diagram}
	\]
	commute.
\end{definition}
\begin{remark}
	Note that $(M,m)$ is a right $M$-module.
\end{remark}
\begin{definition}\label{def-module-map}
	Let $(X,x)$ and $(Y,y)$ be right M-modules.
	A \emph{morphism of modules} from $X$ to $Y$ is
	a map $f: X\to Y$ for which the diagram
	\begin{diagram}
		X\tn M & \rTo^{x} & X \\
		\dTo<{f\tn M} && \dTo>f \\
		Y\tn M & \rTo_{y} & Y
	\end{diagram}
	commutes. The set of such maps will be denoted
	$\Mod_{M}(X,Y)$.
\end{definition}
Kelly proves two versions of his Yoneda Lemma, which he refers
to as `weak' and `strong'. We shall call our corresponding theorems
the `external' and `internal' Cayley Theorem, respectively. The
internal theorem requires some additional properties of $\V$, but
the external one is perfectly general.

\subsection{The external Cayley Theorem}
\begin{thm}[External Cayley]\label{thm-1d-external}
	For every right $M$-module $X$, the natural transformation
	\[
		\phi_{X}: \Mod_{M}(M, X) \to \V(I, X),
	\]
	defined as $\phi_{X}(f) = f\cdot e$, is invertible with
	$\phi_{X}^{-1}(z)$ equal to the composite
	\[
		M \rTo^{\cong} I\tn M \rTo^{z\tn M} X\tn M \rTo^{x} X.
	\]
\end{thm}
\begin{proof}
	Let $f: M\to X$ be a map of modules. We'll first show that
	$\phi_{X}^{-1}(\phi_{X}(f)) = f$: consider the diagram
	\begin{diagram}
		M & \rTo^{\cong} & I\tn M & \rTo^{e\tn M} & M\tn M & \rTo^{f\tn M} & X\tn M \\
		&&& \rdTo_{\cong} & \dTo>m && \dTo>x \\
		&&&& M & \rTo_{f} & X
	\end{diagram}
	The triangle commutes by the left-unit law for the monoid $M$,
	and the square because $f$ is a map of modules. The upper edge
	is $\phi_{X}^{-1}(\phi_{X}(f))$ by definition, and the lower edge is
	equal to $f$.
	
	Now let $z: I\to X$, and consider the diagram
	\begin{diagram}
		&&X \\
		&\ruTo^{z} && \rdTo^{\cong} \\
		I & \rTo_{\cong} & I\tn I & \rTo_{z\tn I}& X\tn I \\
		\dTo<e && \dTo<{I\tn e} && \dTo>{X\tn e} \\
		M & \rTo_{\cong} & I\tn M & \rTo_{z\tn M} & X\tn M & \rTo_{x} & X
	\end{diagram}
	The cells commute by naturality and functoriality of tensor,
	and by the unit condition in the definition of module the upper
	edge is equal to $z$. The lower edge is $\phi_{X}(\phi_{X}^{-1}(z))$
	by definition. Thus $\phi_{X}$ and $\phi_{X}^{-1}$ are indeed
	mutually inverse.
	
	We must also show that $\phi_{X}^{-1}(z)$ is a map of modules,
	so let $z:I\to X$ and consider the diagram
	\begin{diagram}
		M\tn M & \rTo^{\cong} & I\tn M\tn M & \rTo^{z\tn M\tn M} & X\tn M\tn M
			& \rTo^{x\tn M} & X\tn M \\
		\dTo<m &&\dTo>{I\tn m} && \dTo>{X\tn m} && \dTo>m \\
		M & \rTo_{\cong} & I\tn M & \rTo_{z\tn M} & X\tn M & \rTo_{x} & X
	\end{diagram}
	The squares commute, from left to right, by the naturality of the
	left-unit isomorphism, the functoriality of tensor, and the fact
	that $X$ is a module. Thus the outer edge commutes, showing that
	$\phi_{X}^{-1}(z)$ is a map of modules.
\end{proof}
\begin{remark}
	More can be said about $\phi_{X}$, as follows. Each of the sets
	$\Mod_{M}(M, X)$ and $\V(I,X)$ is a right $\V(I,M)$-module
	in a natural way, using the $M$-module structure of $X$.
	Then $\phi_{X}$ is a map of modules with respect to these
	module structures. We omit\footnote{An earlier version of
	this chapter included these details: I removed them, as an
	unneeded distraction.} the details of this, but they are
	quite routine.
\end{remark}
\begin{remark} % \V(I,M) is a monoid
	The set $\V(I, M)$ inherits the monoid structure from $M$:
	its unit is $u:I\to M$, and the product of $a$, $b:I\to M$
	is the composite
	\[
		I \rTo^{\cong} I\tn I \rTo^{a\tn b} M\tn M \rTo^{m} M.
	\]
	This is the \emph{underlying ordinary monoid}
	of the abstract monoid $M$.
\end{remark}

To relate Theorem~\ref{thm-1d-external} to the ordinary
Cayley Theorem, take the module $X$ to be $M$ itself.
Then we have that $\V(I, M)$, the underlying ordinary
monoid of $M$, is isomorphic to $\Mod_{M}(M,M)$, which
is a submonoid of $\V(M,M)$.
%
We should like to be able to say that this $\phi_{M}$
is an isomorphism of monoids, i.e.\ that it preserves
the monoid structure.
\begin{propn}
	The isomorphism
	\[
		\phi_{M}: \Mod_{M}(M,M) \to \V(I, M)
	\]
	is a map of monoids.
\end{propn}
\begin{proof}
	For the unit, $\phi_{M}(1_{M}) = 1_{M}\cdot e = e$.
	For the multiplication, let $f$, $g: M\to M$ be right
	module morphisms: we must show that $\phi_{M}(f\cdot g)$:
	\[
		I \rTo^{e} M \rTo^{g} M \rTo^{f} M
	\]
	is equal to $\phi_{M}(f)\tn\phi_{M}(g)$:
	\[
		I \rTo^{\cong} I\tn I \rTo^{(f\cdot e)\tn(g\cdot e)} M\tn M \rTo^{m} M.
	\]
	Consider the diagram
	\begin{diagram}
		I\tn I & \rTo^{I\tn (g\cdot e)} & I\tn M  & \rTo^{e\tn M} & M\tn M
			 & \rTo^{f\tn M} & M\tn M \\
		\uTo<\cong && \uTo<\cong &\rdTo^{\cong} & \dTo>m && \dTo>m \\
		I  & \rTo_{g\cdot e} & M & \rTo_{1} & M & \rTo_{f} & M
	\end{diagram}
	in which the right-hand square commutes because $f$ is a map of right $M$-modules,
	and the upper triangle by the right-unit law for $M$.
	By the functoriality of tensor, the top edge is equal to $(f\cdot e)\tn(g\cdot e)$,
	so the upper outer edge is $\phi_{M}(f)\tn\phi_{M}(g)$ and the lower
	edge is $\phi_{M}(f\cdot g)$, which are therefore equal as required.
\end{proof}

% \subsection{Coherence issues}
% We have shown that the external Cayley Theorem is true for strict
% monoidal categories, and would like to conclude that it is therefore
% true for arbitrary monoidal categories. This is, of course, overkill
% in the present situation, where it would be trivial to modify our
% proofs to take account of XXXX
% 
\subsection{The internal Cayley Theorem}
The theorem above is external in the sense that it essentially
concerns the set $\V(I, X)$ rather than the module $X$ itself.
If the monoidal category $\V$ is closed, then we can state an
internal version, purely in terms of arrows in $\V$ itself.
%
So let $\V$ be biclosed, i.e.\ suppose we are given
functors
\[\begin{array}{l}
	\lolli: \V\op\times\V\to\V \\
	\illol: \V\times\V\op\to\V,
\end{array}\]
and natural isomorphisms with components
\[\begin{array}{l}
	\curry_{A,B,C}:  \V(A\tn B, C) \cong \V(A, B\lolli C), \\
	\curry'_{A,B,C}: \V(A\tn B, C) \cong \V(B, C\illol A).
\end{array}\]
Then the theorem is:
\begin{thm}[Internal Cayley]\label{thm-1d-internal}
	Let $(X,x)$ be a right $M$-module. Then the diagram
	\begin{diagram}
		X & \rTo^{\curry_{X,M,X}(x)} & M\lolli X & \pile{\rTo^{h} \\ \rTo_{k}}
		 & (M\tn M)\lolli X
	\end{diagram}
	is a coequaliser diagram, where the maps $h$ and $k$ are defined as
	follows. The map $h$ is obtained by currying
	\[
		(M\lolli X)\tn M\tn M \rTo^{\ev^{M}_{X}\tn M} X\tn M \rTo^{x} X,
	\]
	and $k$ is obtained by currying
	\[
		(M\lolli X)\tn M\tn M \rTo^{(M\lolli X)\tn m} (M\lolli X)\tn M \rTo^{\ev^{M}_{X}} X,
	\]
	where the map $\ev^{M}_{X}$ is the result of uncurrying the identity
	on $M\lolli X$.
\end{thm}
%
Although the statement of the theorem uses only the right-closed
structure $\lolli$, the left-closed structure $\illol$ plays a
crucial role in the proof. We will not give a detailed proof here%
\footnote{Again, I did type out a detailed proof. So this is not
	just an excuse for laziness!},
since this is something of a digression, but explain the outline.
The preliminary observations are that:
\begin{enumerate}
	\item For every object $X\in\C$, the object $X\illol X$
	is a monoid in a canonical way, via the definable `internal unit'
	and `internal composition' maps:
	\[\begin{array}{l}
		u: I \to X\illol X, \\
		m: (X\illol X)\tn(X\illol X) \to X \illol X.
	\end{array}\]
	\item A right $M$-module is
	precisely a map of monoids $M\to X\illol X$ for some $X$.
	\item It follows
	from this that a right $M$-module structure on $X$ induces a canonical
	right $M$-module structure on $A\tn X$ for each object $A\in \V$, because
	there is an `internal tensor' map
	\[
		X\illol X \rTo (A\tn X)\illol(A\tn X),
	\]
	which is compatible with the internal unit and compositions.
	\item In a similar
	way, a right $M$-module structure on $X$ induces a canonical
	right $M$-module structure on $X\illol A$, for each object $A$.
\end{enumerate}
Our second observation is trivial to prove: simply curry the diagrams
in Definition~\ref{def-module}. The others are proved in \citet[Section~1.6]{KellyEnriched}.
%
Now for the proof itself: suppose we are given an object $A\in\V$ and
a map $g: A\to M\lolli X$ such that $hg=kg$. We can curry $g$ to get a map
\[
	g': A\tn M \to X,
\]
and it is not hard to check that, since $hg=kg$, this $g'$ is a
map of modules from $A\tn M$ to $X$; where the module structure on
$A\tn M$ is obtained from that of $M$ by point (3) above. Then we
curry $g'$ with respect to the left-closure, to obtain a map
\[
	g'': M \to X\illol A,
\]
which is a map of modules with respect to the module
structure on $X\illol A$ obtained from (4). By the
external Cayley Theorem, $g''$ is thus equal to
\[
	M \rTo^{\cong} I\tn M \rTo^{f\tn M} (X\illol A)\tn M
		\rTo X\illol A
\]
for some unique $f: I \to X\illol A$, where the unlabelled
arrow above comes from the $M$-module structure on $X\illol A$.
From this it can be deduced that $g'$ is equal to
\[
	A\tn M \rTo^{f'\tn M} X\tn M \rTo^{x} X
\]
for some unique $f': A\to X$ (obtained by uncurrying $f$).
%
Thus $g$ is equal to
\[
	A \rTo^{f'} X \rTo^{\curry_{X,M,X}(x)} M\lolli X
\]
for this unique $f'$, which is precisely the universal property of
the equaliser diagram.
\begin{remark}
	Above we have deduced the internal theorem from the external one.
	Conversely, the external theorem can be obtained as a corollary of the internal
	one, under an additional assumption on $\V$. The additional assumption is
	that the functor $\V(I,-): \V\to\Set$ should preserve equalisers. In
	particular, this is always so if $\V$ has small coproducts, because in that
	case $\V$ is \emph{tensored} \citep[in the sense of][Section~2.7]{KellyEnriched}
	as a $\Set$-category, and so the functor $\V(I,-)$ has a left adjoint.
	Then we can obtain the external theorem simply by applying the functor
	$\V(I,-)$ to the equaliser diagram of the internal theorem.
\end{remark}

\section{Cayley's Theorem for Pseudomonoids}
Both these theorems, internal and external, admit generalisation to
the higher-dimensional setting. But since it is sufficient for our
applications, we shall confine ourselves to the external version.

\subsection{Modules for pseudomonoids}
First we must give a suitable definition of $\C$-module, where $\C$ is
a pseudomonoid. In fact, we want to define a bicategory $\Mod_{\C}$ of
right $\C$-modules.
\begin{definition}\label{def-psmod} % Right \C-module
	A \emph{right $\C$-module} $(X,x)$ for the pseudomonoid $\C$
	consists of a 1-cell $x: X\tn\C\to X$ together with invertible
	2-cells
	\begin{diagram}[h=2em]
		&&X\tn\C\\
		&\ruTo^{X\tn J}\\
		X\tn\I & \Arr\Nearrow{\chi^{J}_{X}} & \dTo>x \\
		&\rdTo_{r_{X}} \\
		&&X
	\end{diagram}
	and
	\begin{diagram}
		X\tn(\C\tn\C) & \rTo^{a_{X,\C,\C}} & (X\tn\C)\tn\C
			& \rTo^{x\tn\C} & X\tn\C \\
		\dTo<{X\tn P} && \Nearrow{\chi^{P}_{X}} && \dTo>x\\
		X\tn\C && \rTo_{x} && X
	\end{diagram}
	such that the following two equations hold:
	\[
		\begin{diagram}[tight,vtrianglewidth=1.7em,labelstyle=\scriptstyle]
			&&X\tn\C^{3} && \rTo^{x\tn\C^{2}} && X\tn\C^{2} \\
			&\ldTo^{X\tn\C\tn P} && \rdTo^{X\tn P\tn\C}
			 	&&\Arr\Nearrow{\scriptstyle\chi^{P}_{X}\tn\C} && \rdTo^{x\tn\C} \\
			X\tn\C^{2} && \Right_{\displaystyle X\tn\aa} && X\tn\C^{2}
				&& \rTo^{x\tn\C} && X\tn\C \\
			&\rdTo_{X\tn P} && \ldTo_{X\tn P}
				&& \Arr\Nearrow{\chi^{P}_{X}} && \ldTo_{x} \\
			&&X\tn\C && \rTo_{x} && X
		\end{diagram}
		=
		\begin{diagram}[tight,vtrianglewidth=1.7em,labelstyle=\scriptstyle]
			&&X\tn\C^{3} && \rTo^{x\tn\C^{2}} && X\tn\C^{2} \\
			& \ldTo^{X\tn\C\tn P} &&\sim&&\ldTo^{X\tn P}
				&& \rdTo^{x\tn\C} \\
			X\tn\C^{2} && \rTo^{x\tn\C} && X\tn\C
				&& \Right_{\displaystyle\chi^{P}_{X}} && X\tn\C \\
			&\rdTo_{X\tn P} && \Arr\Nearrow{\chi^{P}_{X}}
				&& \rdTo_{x} && \ldTo_{x} \\
			&&X\tn\C && \rTo_{x} && X
		\end{diagram}
	\]
	and
	\[
		\begin{diagram}[w=4em]
			X\tn \I\tn \C & \rTo^{X\tn J\tn \C} & X\tn \C^{2}
				& \rTo^{x\tn \C} & X\tn \C \\
			&\rdTo_{1}\raise 1em\hbox to1em{$\Arr\Nearrow{X\tn\ll}$\hss}
				& \dTo>{X\tn P} & \Arr\Nearrow{\chi^{P}_{X}} & \dTo>x \\
			&&X\tn \C & \rTo_{x} & X
		\end{diagram}
		=
		\begin{diagram}[w=4em]
			X\tn \I\tn \C & \rTo^{X\tn J\tn \C} & X\tn \C^{2} \\
			&\rdTo_{1} \raise 1em\hbox to 1em{$\Arr\Nearrow{\chi^{J}_{X}\tn\C}$\hss}
				& \dTo>{x\tn \C} \\
			&&X\tn \C\\
			&&\dTo>x \\
			&&X
		\end{diagram}
	\]
\end{definition}
\begin{definition}\label{def-psmod-map} % Map of modules
	Given right $\C$-modules $(X,x)$ and $(Y,y)$, a
	\emph{map of $\C$-modules} from $X$ to $Y$ consists
	of a 1-cell $f: X\to Y$ together with an invertible 2-cell
	\begin{diagram}
		X\tn \C & \rTo^{f\tn \C} & Y\tn \C \\
		\dTo<x & \Arr\Nearrow{\phi^{f}} & \dTo>y \\
		X & \rTo_{f} & Y
	\end{diagram}
	such that
	\[
		\begin{diagram}[tight,vtrianglewidth=1.7em,labelstyle=\scriptstyle]
			&&X\tn\C^{2} && \rTo^{f\tn\C^{2}} && Y\tn\C^{2} \\
			&\ldTo^{X\tn P} && \rdTo^{X\tn\C}
			 	&&\Arr\Nearrow{\scriptstyle\phi^{f}\tn\C} && \rdTo^{y\tn\C} \\
			X\tn\C && \Right_{\displaystyle \chi^{P}_{X}} && X\tn\C
				&& \rTo^{f\tn\C} && Y\tn\C \\
			&\rdTo_{x} && \ldTo_{x}
				&& \Arr\Nearrow{\phi^{f}} && \ldTo_{y} \\
			&&X && \rTo_{f} && X
		\end{diagram}
		=
		\begin{diagram}[tight,vtrianglewidth=1.7em,labelstyle=\scriptstyle]
			&&X\tn\C^{2} && \rTo^{f\tn\C^{2}} && Y\tn\C^{2} \\
			& \ldTo^{X\tn P} &&\sim&&\ldTo^{Y\tn P}
				&& \rdTo^{y\tn\C} \\
			X\tn\C && \rTo^{f\tn\C} && Y\tn\C
				&& \Right_{\displaystyle\chi^{P}_{Y}} && X\tn\C \\
			&\rdTo_{x} && \Arr\Nearrow{\phi^{f}}
				&& \rdTo_{y} && \ldTo_{y} \\
			&&X && \rTo_{f} && Y
		\end{diagram}
	\]
	and
	\[
		\begin{diagram}[h=2em]
			&\rnode{XI}{X\tn \I} & \rTo^{f\tn\I} & Y\tn \I \\
			&\dTo<{X\tn J} & \sim & \dTo>{Y\tn J} \\
			\Right_{\chi^{J}_{X}} & X\tn \C & \rTo^{f\tn \C} & Y\tn \C \\
			&\dTo<x & \Arr\Nearrow{\phi^{f}} & \dTo>y \\
			&\rnode{X}{X} & \rTo_{f} & Y
			%
			\ncarc[arcangle=-90,ncurv=1.3]{->}{XI}{X}\Bput{1}
		\end{diagram}
		=
		\begin{diagram}[h=2em]
			X\tn \I & \rTo^{f\tn \I} & Y\tn \I \\
			&&&\rdTo^{Y\tn J} \\
			\dTo<1 & & \dTo<1 & \Right_{\chi^{J}_{Y}} & Y\tn \C \\
			&&&\ldTo_{y} \\
			X &\rTo_{f} & Y
		\end{diagram}
	\]
\end{definition}
\begin{definition}\label{def-psmod-bicat} % The bicategory Mod_\C
	The bicategory $\Mod_{\C}$ of right $\C$-modules is defined
	as follows. An object is a right $\C$-module, a 1-cell is a
	map of right $\C$-modules, and a 2-cell $\gamma: f\To g: X\to Y$
	is a 2-cell $f\To g$ in $\B$ such that
	\[
		\begin{diagram}[w=4em]
			& \raise -2em\hbox to 0pt{\hss$\Arr\Uparrow{\gamma\tn\C}$} \\
			\rnode{XC}{X\tn \C} & \rTo_{f\tn\C} & \rnode{YC}{Y\tn \C} \\
			\dTo<x & \Arr\Nearrow{\phi^{f}} & \dTo>y \\
			X & \rTo_{f} & Y \\
			%
			\ncarc[arcangle=50]{->}{XC}{YC}\Aput{g\tn\C}
		\end{diagram}
		\qquad=\qquad
		\begin{diagram}[w=4em]
			\\
			\rnode{XC}{X\tn \C} & \rTo^{g\tn\C} & \rnode{YC}{Y\tn \C} \\
			\dTo<x & \Arr\Nearrow{\phi^{g}} & \dTo>y \\
			\rnode{X}{X} & \rTo^{g} & \rnode{Y}{Y} \\
			& \raise 2em\hbox{$\Arr\Uparrow{\gamma}$}
			%
			\ncarc[arcangle=-60]{->}{X}{Y}\Bput{f\tn\C}
		\end{diagram}
	\]
	Composition is defined as in $\B$, and given $f: X\to Y$
	and $g: Y\to Z$, the 2-cell $\phi^{gf}$ is the pasting
	\begin{diagram}
		X\tn \C & \rTo^{f\tn \C} & Y\tn \C
			& \rTo^{g\tn \C} & Z\tn \C\\
		\dTo<x & \Arr\Nearrow{\phi^{f}} & \dTo>y 
			& \Arr\Nearrow{\phi^{g}} & \dTo>z \\
		X & \rTo_{f} & Y & \rTo_{g} & Z
	\end{diagram}
	which is easily verified to satisfy the necessary equations.
\end{definition}

\subsection{Modules via Components}
The calculus of components is very useful here. We shall consider
what the definitions mean in terms of components, which in practice
is essentially the same thing as considering what they imply in the
case $\B = \Cat$.

A right $\C$-module consists of an object $\X$ together with a functor
\[
	x: \X\tn\C\to\X;
\]
we shall write this functor in infix form as $\bullet$. There are also
invertible 2-cells with components
\[
	\alpha^{\bullet}_{X,A,B}: X\bullet(A\tn B) \to (X\bullet A)\bullet B
\]
and
\[
	\rho^{\bullet}_{X}: X\bullet I \to X
\]
where we take $X$ to be a (generic) element of $\X$,
and $A$, $B$ to be elements of $\C$. These are just the
2-cells that were denoted $\chi^{P}$ and $\chi^{J}$ above.
%
The coherence conditions say that the diagrams
\begin{diagram}
	X\bullet(A\tn(B\tn C))
		& \rTo^{\alpha^{\bullet}} & (X\bullet A)\bullet(B\tn C)
		& \rTo^{\alpha^{\bullet}} & ((X\bullet A)\bullet B)\bullet C \\
	\dTo<{X\bullet\alpha} &&&& \uTo>{\alpha^{\bullet}\bullet C} \\
	X\bullet((A\tn B)\tn C) && \rTo_{\alpha^{\bullet}}
		&& (X\bullet(A\tn B))\bullet C
\end{diagram}
and
\begin{diagram}[vtriangleheight=3em]
	X\bullet(I\tn A) && \rTo^{\alpha^{\bullet}} && (X\bullet I)\bullet A \\
	& \rdTo[snake=-1ex]_{X\bullet\lambda_{A}}
		&& \ldTo[snake=1ex]_{\rho^{\bullet}_{X}\bullet A} \\
	&& X\bullet A
\end{diagram}
must commute, for all $X\in\X$ and $A$, $B$, $C\in\C$.
%
It is clear that, in particular, $\C$ itself is a right
$\C$-module, when equipped in the obvious way.

Now, if we have two right $\C$-modules $\X$ and $\Y$, a
map of modules $F: \X\to\Y$ is a 1-cell $F$ equipped with
an invertible 2-cell with components
\[
	F^{\bullet}_{X,A}: F(X\bullet A)\to FX\bullet A
\]
such that the diagrams
\begin{diagram}
	F(X\bullet(A\tn B)) && \rTo^{F^{\bullet}_{X,A\tn B}}
		&& FX\bullet(A\tn B) \\
	\dTo<{F(\alpha^{\bullet}_{X,A,B})}
		&&&& \dTo>{\alpha^{\bullet}_{FX,A,B}} \\
	F((X\bullet A)\bullet B) & \rTo_{F^{\bullet}_{X\bullet A,B}}
		& F(X\bullet A)\bullet B & \rTo_{F^{\bullet}_{X,A}\bullet B}
		& (FX\bullet A)\bullet B
\end{diagram}
and
\begin{diagram}[vtriangleheight=2.5em]
	F(X\bullet I) && \rTo^{F^{\bullet}_{X,I}} && FX\bullet I\\
	&\rdTo[snake=-1ex]_{F(\rho^{\bullet}_{X})}
		&& \ldTo[snake=1ex]_{\rho^{\bullet}_{FX}} \\
	&&FX
\end{diagram}
commute.

Finally, given maps of modules $F$ and $G: \X\to\Y$, a module
2-cell is given by a 2-cell $\gamma: F\to G$ such that the diagram
of components
\begin{diagram}
	F(X\bullet A) & \rTo^{F^{\bullet}_{X,A}} & FX\bullet A \\
	\dTo<{\gamma_{X\bullet A}} && \dTo>{\gamma_{X}\bullet A} \\
	G(X\bullet A) & \rTo_{G^{\bullet}_{X,A}} & GX\bullet A
\end{diagram}
commutes for all $X\in X$ and $A\in \C$.

\subsection{External Cayley for Pseudomonoids}
We shall use the component presentation to prove the External Cayley
theorem.
\begin{propn}[External Cayley for Pseudomonoids]\label{prop-psmoncayley}
	For every right $\C$-module $\X$, the functor
	\[
		\phi_{\X}: \Mod_{\C}(\C,\X)\to \B(\I,\X)
	\]
	defined by $\phi_{\X}(F) = F(I)$ (and in the obvious
	way on 2-cells) is an equivalence of categories, with equivalence-inverse
	$\phi'_{\X}: \B(\I,\X) \to \Mod_{\C}(\C,\X)$ defined as
	\[
		\phi'_{\X}(X()) = X()\bullet-
	\]
	and made into a map of modules
	by the invertible 2-cell $\alpha^{\bullet}_{X(),-,-}$.
\end{propn}
\begin{proof}
	Let $F: \C\to\X$ be a map of $\C$-modules; then
	$\phi'_{\X}(\phi_{\X}(F)) = F(I)\bullet-$
	which, by the natural isomorphism $F^{\bullet}_{I,-}$, is
	naturally isomorphic to $F(I\tn-)$ which, by the right-unit
	isomorphism of $\C$, is naturally isomorphic to $F$.
	
	Let $X()$ (in component notation) be a 1-cell $\I\to\X$.
	Then
	\[
		\phi_{\X}(\phi'_{\X}(X())) = X()\bullet I,
	\]
	which is
	naturally isomorphic to $X()$ by the natural isomorphism
	$\rho^{\bullet}_{X}$.
\end{proof}

\begin{propn}
	The functor $\phi_{\C}: \Mod_{\C}(\C,\C)\to \B(\I,\C)$
	can be equipped with the structure of a strong monoidal
	functor, with respect to the natural monoidal structures
	on the categories $\Mod_{\C}(\C,\C)$ and $\B(\I,\C)$.
\end{propn}
\begin{proof}
	The unit for the monoidal structure of $\Mod_{\C}(\C,\C)$ is
	of course the identity map, and $\phi_{\C}(1) = 1(I) \cong I$.
	For the `tensor' part of the monoidal structure of $\phi_{\C}$,
	we take the composite
	\[
		G(F(I)) \rTo_{\cong}^{G(\lambda_{FI}^{-1})} G(I\tn FI)
			\rTo_{\cong}^{G^{\bullet}_{I,FI}} GI\tn FI.
	\]
	The unit condition holds by the triangle in the definition of map
	of modules, so it remains to show the associativity condition.
	Let $F$, $G$, and $H$ be module maps $\C\to\C$, and consider
	the diagram
	\begin{diagram}
		HGFI & \rTo^{H\lambda_{GFI}} & H(I\tn GFI)
			& \rTo^{H^{\bullet}_{I,GFI}} & HI\tn GFI \\
		\dTo<{HG\lambda_{FI}} && \dTo>{H(I\tn G\lambda_{FI})}
			&& \dTo>{HI\tn G\lambda_{FI}} \\
		HG(I\tn FI) & \rTo_{H\lambda_{G(I\tn FI)}} & H(I\tn G(I\tn FI))
			& \rTo_{H^{\bullet}_{I,G(I\tn FI)}} & HI\tn G(I\tn FI) \\
		\dTo<{H(G^{\bullet}_{I,FI})} && \dTo>{H(I\tn G^{\bullet}_{I,FI})}
			&& \dTo>{HI\tn G^{\bullet}_{I,FI}} \\
		H(GI\tn FI) & \rTo^{H\lambda_{GI\tn FI}} & H(I\tn(GI\tn FI))
			& \rTo_{H^{\bullet}_{I,GI\tn FI}} & HI\tn(GI\tn FI) \\
		\dTo<{H^{\bullet}_{GI,FI}} & \rdTo_{H(\lambda_{GI}\tn FI)}
			& \dTo>{H(\alpha_{I,GI,FI})} \\
		HGI\tn FI && H((I\tn GI)\tn FI) && \dTo>{\alpha_{HI,GI,FI}} \\
		& \rdTo_{H(\lambda_{GI})\tn FI} & \dTo>{H^{\bullet}_{I\tn GI,FI}} \\
		&& H(I\tn GI)\tn FI & \rTo_{H^{\bullet}_{I,GI}\tn FI} & (HI\tn GI)\tn FI
	\end{diagram}
	where the quadrilaterals commute by naturality, the triangle by
	definition of pseudomonoid, and the pentagonal region by the definition
	of morphism of modules.
\end{proof}

So we have shown that, for any pseudomonoid $\C\in\B$, the monoidal
category $\B(\I,\C)$ is monoidally equivalent to $\Mod_{\C}(\C,\C)$.
In the case $\B=\Cat$, this shows that every monoidal category is
monoidally equivalent to a \emph{strict} monoidal category. However
we are more interested in the case $\B=\Prof$, and some of the
implications in this case are explored in the next chapter.

% \subsection{Remarks on the unit conditions}\label{s-unit-remarks}
% The definitions above are conventional in style. However,
% we have the same sort of redundancy that we saw, for pseudofunctors
% and pseudonatural transformations, in Section~\chref{Bicats}{s-identities}.
% This time, the redundancy turns out to be essential to some of our later
% results.
% 
% For a start, we have:
% \begin{propn}
% 	The unit condition of Definition~\ref{def-psmod-map}
% 	is redundant.
% \end{propn}
% \begin{proof}
% 	In the situation $\B=\Cat$, the proof is via the diagram
% 	\begin{diagram}
% 	F(X\bullet(I\tn A)) && \rTo^{F^{\bullet}_{X,I\tn A}}
% 		&& FX\bullet(I\tn A) \\
% 	& \rdTo(0,4)<{F(\alpha^{\bullet}_{X,I,A})}
% 		\rdTo[snake=1em](1,2)^{F(X\bullet\lambda_{A})}
% 		& & \ldTo[snake=-1em](1,2)^{FX\bullet\lambda_{A}}
% 		\ruTo(0,4)<{\alpha^{\bullet}_{FX,I,A}} \\
% 		& F(X\bullet A) & \rTo^{F^{\bullet}_{X,A}} & FX\bullet A \\
% 	 \ruTo[snake=.5em](1,2)_{F(\rho^{\bullet}_{X}\bullet A)}
% 		&& \ruTo[snake=-.5em](1,2)<{F(\rho^{\bullet}_{X})\bullet A}
% 		&& \luTo(1,2)<{\rho^{\bullet}_{FX}\bullet A} \\
% 	F((X\bullet I)\bullet A) & \rTo_{F^{\bullet}_{X\bullet I,A}}
% 		& F(X\bullet I)\bullet A & \rTo_{F^{\bullet}_{X,I}\bullet A}
% 		& (FX\bullet I)\bullet A
% 	\end{diagram}
% 	We observe that, since the outside commutes and all the
% 	other cells commute, and since the arrows are all invertible,
% 	the lower triangle must also commute. Then let $A=I$ and use
% 	the fact that the functor $-\bullet I$ is full and faithful.
% 	
% 	The same proof works in the general setting: 
% \end{proof}
\end{thesischapter}